---
title: "Counihan_rmarkdown_example"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Bus stop, wet day, she's there, I say, please share my umbrella

## header two

**Bus stop, bus goes, she stays, love grows, under my umbrella**

*italics*

1.yes
2.No
3.Maybe
$/

create r chunk
```{r}```

#are short cuts to creating r chunks
command option i
cntrl alt i


```{r}
x<-c(1:10)
x
```
 
$\sum (n-1)$

```{r}
library(readr)
```

## **Introduction**

- read in data

```{r chunk1, message=FALSE}
bg_chem <- read.csv("BGchem2008data.csv")
```

These data came from [Tweedie, 2009](https://doi.org/10.18739/A25T3FZ8X)

## **Analysis**

- calculate summary statistics
- calculate mean Redfield ratio
- plot Redfield ratio

I am doing the following analyses as an example

```{r}
nitrate <- mean(bg_chem$NO3)
nitrite <- mean(bg_chem$NO2)
amm <- mean(bg_chem$NH4)
phos <- mean (bg_chem$P) 
```

Here is the redfield analyses

```{r}
ratio <- (nitrate+nitrite+amm)/phos
```

we calculated the redfield ration to be `r round (ratio)`

- plot redfile ratio

```{r}
plot(bg_chem$P, bg_chem$NO3+bg_chem$NO2+bg_chem$NH4)
```

```{r}
plot(bg_chem$NO3, bg_chem$NO3)
```

```{r}
lm(bg_chem$CTD_Depth ~ bg_chem$CTD_Temperature)
```